TacticToe: Learning to Prove with Tactics

### 2018-08-15 review_response.tex

\section*{Reviewer 1}

\begin{leftbar}
No data is provided to help other researchers reproduce this experiment.  I 
consider this is a flaw of the paper.  I think the paper should be improved in 
the direction of making the experiment reproducible by other researchers, as 
much as possible. The paper provides numerical evaluation of its results, 
mostly in the form of 
percentage of success under a given timeout. I would also be interesting to 
know how much it takes to re-run the whole process of learning and then using 
for the complete database.
\end{leftbar}

\section*{Reviewer 2}

\begin{leftbar}
The only reservation I have with the paper is that it is not clear to me 
whether and how the proof tool is able to generate two commonly-used tactics. 
Firstly, generating witnesses to existential goals using \texttt{EXISTS\_TAC 
tm}. If these 
tactics are out of scope for the proof tool, then are all goals containing 
existential
quantifiers impossible for the tool to prove? Secondly, reducing a goal using 
an implication theorem using \texttt{MATCH\_MP\_TAC thm}. Often such 
implication 
theorems 
are
highly specific to a single theory or even theorem, so how can tactics like 
this be effectively learned? In my opinion the paper would be improved by a 
brief
discussion on how these tactics could be learned, either in the present or a 
future system.
\end{leftbar}

### 2018-08-15 tactictoe_jv.tex
Reproducibility paragraph

\subsection{Tuning \tactictoe}\label{sec:tuning}

We optimize \tactictoe by tuning parameters of six different techniques:
the timeout of tactics, orthogonalization, abstraction, MCTS policy, MCTS
evaluation and ATP integration. During training, optional techniques such as
orthogonalization may also be turned off completely.
\tactictoe also includes other important techniques which are run with their
default parameters: feature extraction, prediction
algorithms, number of premises for ATPs and MCTS evaluation radius (set by default to
10).
By choosing a set of parameters, we create a strategy for
\tactictoe that is evaluated on our training set of 273 theorems. And the
strategy with the highest number of re-proven theorems is selected for
a full scale evaluation.

>>>>

\paragraph{Reproducibility}
The \tactictoe project is part of the \holfour distribution 
which can be downloaded at \url{https://github.com/HOL-Theorem-Prover/HOL}.
The \tactictoe modules can be found in the directory
\url{HOL/src/tactictoe}. The README explains how to launch the recording 
process (which includes learning techniques such as orthogonalization),
use \tactictoe interactively and run a re-proving experiments on a theory. The 
recording process takes less than eight hours. An upper bound for 
the time necessary for the final experiment can be given by the formula:
\[\mathit{number\ of\ theorems} \times \mathit{timeout} = 7164 \times 60\ 
\mathit{seconds} = 
4.975\ \mathit{days}\] which translate in practice
to about $2.5\ \mathit{days}$ because successful searches stop before reaching 
the timeout. And finally, by running this experiment on 20 cores, we cut down 
the actual total time requirement to a few hours.

\subsection{Tuning \tactictoe}\label{sec:tuning}
We optimize \tactictoe by tuning parameters of six different techniques:
the timeout of tactics, orthogonalization, abstraction, MCTS policy, MCTS
evaluation and ATP integration. During training, optional techniques such as
orthogonalization may also be turned off completely.
\tactictoe also includes other important techniques which are run with their
default parameters: feature extraction, prediction
algorithms, number of premises for ATPs and MCTS evaluation radius (set by default to
10).
By choosing a set of parameters, we create a strategy for
\tactictoe that is evaluated on our training set of 273 theorems. And the
strategy with the highest number of re-proven theorems is selected for
a full scale evaluation.
